---
title: "artists_draft"
author: "Nosa Lawani"
date: "3/16/2023"
output: html_document
---

```{r setup, include=FALSE, message= FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
library(rmarkdown)
read_csv("moma_files/collection-master/Artists.csv") %>% 
  mutate(Gender = str_replace_all(Gender, "^male", "Male"),
         Gender = str_replace_all(Gender, "^female", "Female"), 
         Gender = str_replace_all(Gender, "Non-binary", "Non-Binary")) -> x
```

# Artists 

### Overview

There are 15,243 different artists in the MoMa data set.
They and their unique characteristics are listed in a single file, Artists.csv

77 of these artists have a name identical to that of another artist in the dataset. 
Many of these are 'Unidentified'. The others, in most cases, appear to be father and son.

```{r, duplicate artists names, message= FALSE, warning=FALSE}
read_csv("moma_files/collection-master/Artists.csv") %>% 
  select(-3) %>% 
  select(DisplayName) %>% 
  filter(duplicated(DisplayName) == TRUE) %>% 
  arrange(DisplayName) -> y

paged_table(read_csv("moma_files/collection-master/Artists.csv") %>% 
 filter(DisplayName %in% y$DisplayName) %>% 
  arrange(DisplayName))
```

### Nationality 

There are 120 different artist nationalities. 
There are 2,472 artists for whom a nationality is not given

```{r, nationality_summary}
x %>% 
  mutate(Nationality = replace_na(Nationality, "NA")) %>% 
  group_by(Nationality) %>% 
  summarize(number_of_artists = n()) %>% 
  arrange(desc(number_of_artists)) %>% 
  filter(number_of_artists >= 200) %>% 
  ggplot(aes(y = fct_reorder(Nationality, number_of_artists), x = number_of_artists)) +
  geom_col() +
  labs(title = "Top Artist Nationalities",
       subtitle = "Nearly 2500 Artists have a blank (i.e. NA) Nationality Field",
       x = "",
       y = "",
             caption = "Source: MoMA") 

paged_table(x %>% 
  mutate(Nationality = replace_na(Nationality, "NA")) %>% 
  group_by(Nationality) %>% 
  summarize(`Number of Artists` = n()) %>% 
    arrange(desc(`Number of Artists`)))
```

### Artist Birth Year

Most artists are born in the 20th century. 
There are 3,642 artists for whom a birth year is not given. 

```{r, birth_year summary}
x %>% 
  filter(BeginDate >= 1700) %>% 
  ggplot(aes(x = BeginDate)) +
  geom_histogram(color = "white", binwidth = 20, boundary = 1900) +
  scale_x_continuous(breaks = seq(1700, 2030, by = 20)) +
  scale_y_continuous(breaks = seq(0, 3000, by = 500)) +
  labs(title = "Count of Artist Birth Years", 
       subtitle = "Not counted below are 3642 artists without birth years and 1 artist born in 1181.",
       x = "Birth Years", 
       y = "Count", 
       caption = "Source: MoMA")
```

### Gender

Most artists are male. 
There are 3,165 artists for whom a gender is not given.

```{r, gender}
x %>% 
  mutate(Gender = replace_na(Gender, "NA")) %>% 
  ggplot(aes(y = fct_rev(fct_infreq((Gender))))) +
  geom_bar() +
  labs(title = "Gender of Artists", 
       subtitle = "Over 2500 artists have no listed gender", 
       x = "",
       y = "", 
       caption = "Source: MoMA")

x %>% 
  filter(BeginDate >= 1700) %>% 
  mutate(Gender = replace_na(Gender, "NA")) %>% 
  mutate(Gender = factor(Gender, levels = c("Female", "Male", "Non-Binary", "NA"))) %>% 
  ggplot(aes(x = BeginDate, fill = fct_rev(Gender))) +
  geom_histogram(color = "white", binwidth = 20, boundary = 1900) +
  scale_x_continuous(breaks = seq(1700, 2030, by = 20)) +
  scale_y_continuous(breaks = seq(0, 3000, by = 500)) +
  labs(title = "Artist Gender and Birth Year", 
       subtitle = "Not counted below are 3642 artists without birth years and 1 artist born in 1181.",
       x = "Birth Years", 
       y = "Count", 
       fill = "Gender",
       caption = "Source: MoMA") +
  scale_fill_manual(values = c(Female = "pink", Male = "light blue", 'Non-Binary' = "black", 'NA' = "grey"))
```
