---
title: "Exhibitions Draft"
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(rmarkdown)
```

```{r, warning = FALSE, message = FALSE}
read_csv("moma_files/exhibition/MoMaExhibitions1929to1989.csv", ) -> x 
```

### Original Table
```{r}
paged_table(x)
```

### Number and Size of Exhibitions

Dataset contains rows of information for each constituent (e.g. artists, curators, institutions) involved in a MoMA exhibition.
1735 exhibitions. 
Average of 20 unique constituents per exhibition. The smallest exhibition has 1 constitutent and the largest has 338. 

```{r, warning = FALSE, message = FALSE}
# x %>% 
#   group_by(ExhibitionNumber) %>% 
#   summarize(n())
# 
# x %>% 
#   group_by(ExhibitionNumber) %>% 
#   summarize(n()) %>% 
#   summarize(mean(`n()`), min(`n()`), max(`n()`))
```

### Constituents of Exhibitions

There are roughly 32,000 'constituents' in the data. Most broadly, constituents are either 
of the type, Individuals or Institutions. Roughly 93 percent are individuals. 

Each constituent is also assigned a role. 94% have the role of artists. 
The next most common role, with 4.3% of consitutents, is curator. Others include 
installer, competiton judge, designer, arranger, and preprer. Another field in the 
data set specifies the constituent's role in the press release; this field 
includes a few more, uncommon options.  

```{r, warning = FALSE, message = FALSE}
# x %>% 
#   group_by(ExhibitionRole) %>% 
#   summarize(n()) %>% 
#   arrange(desc(`n()`)) %>% 
#   mutate(percent = `n()` / sum(`n()`))
# 
# x %>% 
#   group_by(ExhibitionRoleinPressRelease) %>% 
#   summarize(n()) %>% 
#   arrange(desc(`n()`)) %>% 
#   mutate(percent = `n()` / sum(`n()`))
# 
# x %>% 
#   group_by(ConstituentType) %>% 
#   summarize(n()) %>% 
#   arrange(desc(`n()`)) %>% 
#   mutate(percent = `n()` / sum(`n()`))
```

The vast majority of constituents are listed in a given exhibition only once. If a constituent
is listed in an exhibition more than once, it is usually because he has multiple 
roles, e.g. Designer and Artist. 

```{r, warning = FALSE, message = FALSE}
# x %>% 
#   group_by(ConstituentID, ExhibitionID) %>% 
#   summarize(n()) %>% 
#   arrange(desc(`n()`)) %>% 
#   filter(is.na(ConstituentID) == FALSE) %>% 
#   filter(is.na(ExhibitionID) == FALSE) %>% 
#   filter(`n()` > 1) %>% 
#   select(1:2) %>% 
#   semi_join(x, .) %>% 
#   select(ExhibitionID, ConstituentID,  DisplayName, ExhibitionRole, ExhibitionRoleinPressRelease, ExhibitionTitle, ExhibitionBeginDate, ExhibitionEndDate, ConstituentType, ConstituentBeginDate, ConstituentEndDate) %>% 
#   arrange(ExhibitionID, ConstituentID) %>% 
#   select(ConstituentID) %>% 
#   unique()
```

Over 60% of artists have only been exhibited once.
The top 5% of artists make up 46% of the total number of individual artist exhibitions.

Percentiles: Number of Times Artists have been Exhibited

```{r, warning = FALSE, message = FALSE}
options(width = 500)

total_artists_exhibited = 25458 + 7079

x %>% 
  filter(ExhibitionRole == "Artist") %>% 
  group_by(ConstituentID, DisplayName) %>% 
  summarize(n()) %>% 
  arrange(desc(`n()`)) %>% 
  ungroup() -> d

quantile(d$`n()`, c(seq(0, .9, .1), .95, .99, 1))

# d %>% 
#   group_by(`n()` >= 9) %>% 
#   summarize(sum(`n()` / total_artists_exhibited))
``` 

```{r, warning = FALSE, message = FALSE}
d %>% 
  slice(1:10) %>% 
  ggplot(aes(`n()`, fct_reorder(DisplayName, `n()`))) +
  geom_col() +
  labs(title = "Top 10 Artists by Most Times Exhibited", 
       x = "", 
       y = "", 
       caption = "Source: MoMA")
```

### Dates of Exhibitions: Only until 1989

The data set contains exhibitions from the MoMA's opening in 1929 up until 1989. 
There are an average of 29 exhibitions per year. 
The year with the fewest exhibitions had 2. The year with the most had 53. 

The average duration of an exhibition is 71 days. 

```{r, warning = FALSE, message = FALSE}
x %>% 
  group_by(ExhibitionID, ExhibitionBeginDate) %>% 
  summarize(n()) %>% 
  mutate(ExhibitionBeginDate = year(mdy(ExhibitionBeginDate))) %>% 
  ggplot(aes(x = ExhibitionBeginDate)) +
  geom_histogram(boundary = 1940, binwidth = 5, color = "white", closed = "right")  +
  scale_x_continuous(breaks = seq(1925, 1990, 5)) +
  labs(title = "Number of Exhibitions for every 5 Years at the MoMA", 
       subtitle = "Data for exhibitions is from 1929 to 1989.", 
       y = "Number of Exhibitions", 
       x = "",
       caption = "Source: MoMA")

# x %>% 
#   group_by(ExhibitionID, ExhibitionBeginDate) %>% 
#   summarize(n()) %>% 
#   mutate(ExhibitionBeginDate = year(mdy(ExhibitionBeginDate))) %>% 
#   group_by(ExhibitionBeginDate) %>% 
#   summarize(n()) %>% 
#   summarize(mean(`n()`), max(`n()`), min(`n()`))
```

### Gross Quality Check:Percent of blank values in each column
```{r, warning = FALSE, message = FALSE}
paged_table(
  x %>% 
  summarize(across(everything(), ~ sum(is.na(.)) / length(.))) %>% 
  mutate(across(everything(), ~paste0(round(.*100, 5), "%")))
  )
```


