---
title: "MoMA Data Set Overview"
description: |
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
```

```{r, warning = FALSE, message = FALSE}
read_csv("moma_files/collection-master/Artworks.csv", ) -> x

x %>% 
  filter(!(CreditLine %in% c("Gift of the artist", "Purchase", "Anonymous gift", "Given anonymously", "Gift of the designer", "Gift of the architect", "Gift of the designers", "Gift of the architects")) == TRUE) %>% 
  filter(is.na(CreditLine) == FALSE) %>% 
  filter(is.na(DateAcquired) == FALSE) %>% 
  mutate(DateAcquired = year(DateAcquired)) %>% 
  group_by(CreditLine) %>% 
  summarize(range = (max(DateAcquired) - min(DateAcquired)) + 1, n()) -> z
```

## Executive Summary 

The MoMA dataset is likely the most complete available source for information on
the artwork, artists, exhibitions of the museum. 

The dataset has information in most of the preliminary categories of information
identified for the project, particularly, institutions, artists, artowrks, 
curators, supporters, older exhibitions, and dates.

The dataset, however, also lacks information in some of these preliminary categories  of information:

* While the information on artworks and artists is current and regularly updated, 
information on exhibitions is only available for exhibitions that occurred in 1989 
or before.

* Outside of the department of a work, no further "collection" or subsample is
given in the dataset as it is. 

* There is no information on ticket sales of exhibitions or their critical acclaim. 

* Aside from the credit lines attached to specific works, there is no information 
in the dataset on acts of donation. 

* Few fields are 100% complete or standardized. These missing fields can pile up 
(v.s. below with curators). Even when information is available in the vast majority 
of cases, occasional gaps and errors will limit accuracy. 


### 1. Institutions

The data set gives information on a single institution: The Modern Museum of American Art (MoMA)

### 2. Artists

The dataset includes a thorough (v.i.) listing of artists with artworks in the MoMA. 
For most, the artist's name, nationality, gender, birth year, and death year are
in the data set. 

### 3. Artworks

The dataset includes a thorough listing of artworks in the MoMA. According to  
[documentation](https://github.com/MuseumofModernArt/collection/blob/master/README.md) provided by the MoMA with the dataset, the Museum's website contains around 98,000 records, whereas the dataset contains around 140,000.

For most artworks, the title of the work, the artist, the date, classification (painting, drawing, etc.), 
 medium (e.g. "Ink and cut-and-pasted painted pages on paper"), some form of dimensions, 
credit line (e.g. Purchase; Gift of the architect in honor of Lily Auchincloss), 
department and date of acquisition are avilable in the data set. 

### 4. Curators

There is someone listed in the role of curator for about 75% of the 1,735 exhibitions 
in the dataset. For most of these, a role as described in the press release are available
in the data set.

For roughly half of these, nationality, gender, birth year, and death year are 
available in the data set.

For a minority of these, senior titles at the museum, dates of tenure of those titles
are available in the data set. 


```{r}

# move this calculation
# x %>%
#   group_by(ExhibitionNumber, ExhibitionTitle) %>%
#   mutate(curator = if_else(str_detect(ExhibitionRole, "[Cc]urator"), TRUE, FALSE)) %>%
#   summarize(sum_curator = sum(curator)) %>%
#   group_by(sum_curator) %>%
#   summarize(n()) %>%
#   mutate(percent = `n()` / sum(`n()`))

# x %>% 
#   filter(ExhibitionRole == "Curator") %>% 
#   summarize(across(everything(), ~ sum(is.na(.)) / length(.))) %>% 
#   mutate(across(everything(), ~paste0(round(.*100, 5), "%")))
``` 

### 5. Collections

The only subsample in the dataset as it is given is Department. 

One could, based on other information in the dataset, create and describe 
characteristics of a subsample or "collection" of works, e.g. works by American artists.

### 6. Supporters

About 99% of artworks in the MoMA have a listed credit line. About 82% of these point
to an individual donor or foundation. Examples of those that do not themselves point 
to an individual include "Purchase" or "Gift of the artist."

About half of credit lines pointing to individual donors or foundations have donated only
a single work. The top 10% of credit lines by most works in the museum account for 
65% of works in the museum.

Percentiles: Works per Credit Line

```{r}
options(width = 500)
quantile(z$`n()`, probs = c(seq(0, .9, .1), .95, .99, 1))
```

By taking information from works associated with the credit line, one is also able 
to find information on when and for how long a credit line was active.

### 7. Exhibitions

The dataset provides a list of all MoMA exhibitions form 1929 to 1989. For most of these,
the title of the exhibition, the opening and closing dates are available. 

People and institutions involved in each exhibition, their roles (e.g. artists, curators, designers), 
and other information (v.s.) are available.

### 8. Ticket Sales

The dataset contains no information on tickets sold by exhibitions. 

### 9. Critical Acclaim

The dataset contains no information on critical acclaim of exhibitions or other events. 

### 10. Dates

The following is a list of all dates available in the dataset:

* Artist Birth Year and Death Year
* Year of Creation of Artwork
* Year of Acquisition of Artwork
* Opening and Closing Date (MDY) of Exhibition
* Birth and Death Year of Entity involved in Exhibition
* Start and End Year of Tenure of Museum Directors and Department Heads
* Birth and Death Year of Museum Directors and Department Heads

### 11. Donations

Outside of the names of credit lines associated with specific works (v.s.), there
is no information on specific contributions to the institution. 



