---
title: "Artwork Data"
author: "Nosa Lawani"
date: "3/16/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(rmarkdown)

read_csv("../moma_files/collection-master/Artworks.csv") -> x 
```

```{r, warning = FALSE, message = FALSE}

# Note: number of artists here is not the same asd artists csv. Odd. 

# x %>% 
#   select(ConstituentID) %>% 
#   separate_rows(ConstituentID, sep = ", ") %>% 
#   unique() 

total <- 140848
```

### Original Table

```{r}
paged_table(x)
```

### Artists and Artworks

13,736 artists have work of art attributed to them in the MoMa dataset. Note that this number is fewer than the number of artists in the artists spreadsheet.

Over 50% of artists have a single work of artwork in the MoMA. 
The top 1% of account for 41% of artworks in the MoMA.

Percentiles: Works per Artist
```{r, warning = FALSE, message = FALSE}
x %>% 
  group_by(Artist, ConstituentID) %>% 
  summarize(`Number of Works per Artist` = n()) %>% 
  filter(is.na(ConstituentID) == FALSE) %>% 
  arrange(desc(`Number of Works per Artist`)) %>% 
  ungroup()-> y

round(quantile(y$`Number of Works per Artist`, c(seq(0, .9, .1), .95, .99, 1)), 0)

# y %>%
#   group_by(`Number of Works per Artist` >=  144) %>%
#   summarize(sum = sum(`Number of Works per Artist`)) %>%
#   mutate(percent = sum / sum(sum))
```

```{r, warning = FALSE, message = FALSE}
y %>% 
  slice(1:10) %>% 
  ggplot(aes(`Number of Works per Artist`, fct_reorder(Artist, `Number of Works per Artist`))) +
  geom_col() +
  labs(title = "Top 10 Artists by Most Works in the MoMA", 
       x = "", 
       y = "",
       caption = "Source: MoMA")
```


### Dates of Artwork: Requires Cleaning

Most works of art have dates. These, however, sometimes have more information than just a 4 digit year (e.g. c. 1930, 1930-32, after 1930, 1930, published 1932.). Simplification of this field will be required before further analysis. 

```{r, warning = FALSE, message = FALSE}
# x %>% 
#   select(Date) %>% 
#   mutate(circa = if_else(str_detect(Date, "c\\."), TRUE, FALSE),
#          Date = str_replace_all(Date, "c\\.[ ]*", "")) %>% 
#   mutate(extra_date_bool = if_else(str_detect(Date, "^[0-9]*[-–][0-9]*$"), TRUE, FALSE),
#          extra_date = if_else(str_detect(Date, "^[0-9]*[-–][0-9]*$"), str_replace_all(Date, "[0-9]*(?=[-–])", ""), ""),
#          extra_date = na_if(extra_date, ""),
#          Date = str_replace_all(Date, "[-–].*", "")) %>% 
#   mutate(unknown = if_else(Date == "Unknown", TRUE, FALSE),
#          Date = na_if(Date, "Unknown")) %>% 
#   mutate(after = if_else(str_detect(Date, "^[Aa]fter "), TRUE, FALSE),
#          Date = if_else(str_detect(Date, "^[Aa]fter "), str_replace_all(Date, "[Aa]fter ", ""), Date)) %>% 
#   filter(str_detect(Date, "[^0-9]"))
#   
# 
# x %>% 
#   filter(str_detect(Date, "c\\."))
```

### Classifications of Artworks

There are 36 classifications of works of art. Most classifications are based on medium, with the exception of Frank Llloyd Wright Archive.
Only 1 work of art has no classification. 678 works of art are noted as "not assigned".

```{r, warning = FALSE, message = FALSE}
x %>% 
  group_by(Classification) %>% 
  summarize(number = n()) %>% 
  arrange(desc(number)) %>% 
  slice(1:20) %>% 
  ggplot(aes(number, fct_reorder(Classification, number))) +
  geom_col() +
  scale_x_continuous(breaks = seq(0, 40000, 3000), minor_breaks = NULL) +
  labs(title = "Top 20 Classifications of Artworks in MoMA Dataset", 
       y = "Classification", 
       x = "Number of Works of Art", 
       caption = "MoMA")
```

### Media: An Unwieldy Category 

There are 21,641 distinct classes of media. 

```{r, warning = FALSE, message = FALSE}
x %>% 
  group_by(Medium) %>% 
  summarize(n()) %>% 
  arrange(desc(`n()`)) %>% 
  mutate(Medium = replace_na(Medium, "NA")) %>% 
  slice(1:30) %>% 
  ggplot(aes(y = fct_reorder(Medium, `n()`), x = `n()`)) +
  geom_col() +
  labs(title = "Top 30 Media of MoMA Artworks", 
       subtitle = "The top 30 media contain 30% of the museum's artworks", 
       x = "Number of Artworks", 
       y = "",
       caption = "Source: MoMA")
```


```{r, warning = FALSE, message = FALSE}
# x %>% 
#   group_by(Department) %>% 
#   summarize(n()) %>% 
#   arrange(desc(`n()`)) %>% 
#   geom
```

### Credit Lines

There are over 7200 distinct Credit Lines. 

These include Credit Lines such as "Gift of the artist" which, though they are the same in the data, indicate more than one real-life donor. "Purchase" is another  common Credit Line that does not indicate a real life donor. 17% of works belong to such credit lines. 

Roughly 1% of works do not have a credit line given in the dataset.

```{r, warning = FALSE, message = FALSE}

# Note anonymous gift and given anonymously, such things must be cleaned
x %>%
  filter(!(CreditLine %in% c("Gift of the artist", "Purchase", "Anonymous gift", "Given anonymously", "Gift of the designer", "Gift of the architect", "Gift of the designers", "Gift of the architects")) == TRUE) %>%
  filter(is.na(CreditLine) == FALSE) %>%
  filter(is.na(DateAcquired) == FALSE) %>%
  mutate(DateAcquired = year(DateAcquired)) %>%
  group_by(CreditLine) %>%
  summarize(range = (max(DateAcquired) - min(DateAcquired)) + 1, n()) -> z
# 
# x %>% filter(!(CreditLine %in% c("Gift of the artist", "Purchase", "Anonymous gift", "Given anonymously", "Gift of the designer", "Gift of the architect", "Gift of the designers", "Gift of the architects")) == FALSE) %>% 
#   summarize(n(), n() / total)
# 
# x %>% 
#   filter(is.na(CreditLine) == TRUE) %>% 
#   summarize(n(), n() / total)
```

Of the credit lines that do point to individual donors (henceforth individual credit lines), the majority have only 
a single majority in the museum. The list of percentiles below show that fewer than 50%
of individual credit lines have more than 1 work, and only 10% of individual credit lines have more than 17 works.

The top 10% of individual credit lines are responsible for 10% for 65% of works in the MoMA.

Percentiles: Works per Credit Line
```{r, warning = FALSE, message = FALSE, layout = "l-page", fig.width = 10, fig.length = 8}
quantile(z$`n()`, probs = c(seq(0, .9, .1), .95, .99, 1))

# z %>% 
#   filter(`n()` >= 17) %>% 
#   summarize(sum(`n()`), sum(`n()`) / total)

# z %>% 
#   arrange(desc(`n()`)) %>% 
#   slice(1:10) %>% 
#   ggplot(aes(x= `n()`, y = fct_reorder(CreditLine, `n()`))) +
#   geom_col() +
#   labs(title = "Top Credit Lines by Number of Works", 
#        x = "", 
#        y = "", 
#        caption = "Source: MoMA")
```

Most credit lines are only "active" for one year. The length of time for which a credit line is active 
is a measure obtained by subtracting the year in which the credit line's last work was acquired
from the year in which the credit line's first work was acquired, then adding 1. 
The list below gives percentiles for the number of years for which a credit line is active.

Percentiles: Years Active for all Credit Lines
```{r, warning = FALSE, message = FALSE}
quantile(z$range, probs = c(seq(0, .9, .1), .95, .99, 1))
```

Credit lines that have more works in the museum also tend to be credit lines that have longer lifespans. 

Percentiles: Years Active the 10% of Credit Lines with the Most Works
```{r, warning = FALSE, message = FALSE}
round(quantile((z %>% filter(`n()` >= 17))$range, probs = c(seq(0, .9, .1), .95, .99, 1)), digits = 0)
```

### Gross Quality Check: Percent of blank values in each column

```{r, warning = FALSE, message = FALSE}
  x %>% 
  select(-c(ArtistBio, Nationality, BeginDate, EndDate, Gender)) %>% 
  summarize(across(everything(), ~ sum(is.na(.)) / length(.))) %>% 
  mutate(across(everything(), ~paste0(round(.*100, 5), "%"))) %>% 
  unlist()

x %>% 
  group_by(is.na(`Circumference (cm)`)) %>% 
  summarize(n())

x
```















